Solent region: Test Maps

### 2021-07-30 Solent_Mapping_v2.Rmd
Added in the title for the idfference in non domestic gas at MSOA level from 2010 to 2019

```{r Loading in the MSOA gas consumption data for industry }
# gas consumption data for industry at MSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/MSOA_NonDom_Gas_2019.csv")
msoa_gasDatanondom <- readr::read_csv(inFile)
head(msoa_gasDatanondom)
```

@@

>>>>

### Mapping Gas
```{r Loading in the MSOA gas consumption data for industry }
# gas consumption data for industry at MSOA level (pre downloaded)
inFile <-paste0(dataFolder, "energy/MSOA_NonDom_Gas_2019.csv")
msoa_gasDatanondom <- readr::read_csv(inFile)
head(msoa_gasDatanondom)
```

@@

####Mapping the difference in non domestic gas from 2010 to 2019
